Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill

### 2019-01-28 reports/preprint/preprint.tex
update preprint for OSF conventions

% Page setup
\usepackage[
    margin=1in
]{geometry}

@@

\usepackage[acronym]{glossaries}
\makeglossaries
\newacronym{cca}{CCA}{canonical correlation analysis}
\newacronym{ecmwf}{ECMWF}{European Centre for Medium-Range Weather Forecasts}
\newacronym{enso}{ENSO}{El Ni\~{n}o-Southern Oscillation}
\newacronym{eof}{EOF}{empirical orthogonal function}
\newacronym{iri}{IRI}{International Research Institute for Climate and Society}
\newacronym{hxlr}{HXLR}{heteroscedastic extended logistic regression}
\newacronym{lprb}{LPRB}{Lower Paraguay River Basin}
\newacronym{mjo}{MJO}{Madden-Julian Oscillation}
\newacronym{mos}{MOS}{model output statistics}
\newacronym{sallj}{SALLJ}{South American low-level jet}
\newacronym{pcr}{PCR}{principal components regression}
\newacronym{s2s}{S2S}{sub-seasonal to seasonal}
\newacronym{sacz}{SACZ}{South Atlantic Convergence Zone}
\newacronym{scad}{SCAD}{South Central Atlantic Dipole}
\newacronym{sst}{SST}{sea-surface temperature}
\newacronym{xlr}{XLR}{homoscedastic extended logistic regression}
\newacronym{wt}{WT}{weather type}

@@

\date{}
\title{Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill}
\author[1,2]{James Doss-Gollin}
\author[3,4]{\'{A}ngel G. Mu\~{n}oz}
\author[4]{Simon J. Mason}
\author[5,6]{Max Past\'{e}n}
\affil[1]{Department of Earth and Environmental Engineering, Columbia University}
\affil[2]{Columbia Water Center}
\affil[3]{Atmospheric and Oceanic Sciences (AOS), Princeton University}
\affil[4]{International Research Institute for Climate and Society (IRI), The Earth Institute, Columbia University.}
\affil[5]{Direcci\'{o}n de Meteorolog\'{i}a e Hidrolog\'{i}a, Paraguay}
\affil[6]{Facultad Polit\'ecnica, Universidad Nacional de Asunci\'{o}n, Paraguay}

@@

This is a pre-print of the paper ``Heavy rainfall in Paraguay during the 2015-16 austral summer: causes and sub-seasonal-to-seasonal predictive skill'', by James Doss-Gollin, \'{A}ngel G. Mu\~{n}oz, Simon J. Mason, and Max Past\'{e}n, published in Journal of Climate.
You can find the final, type-set version at \url{https://journals.ametsoc.org/doi/abs/10.1175/JCLI-D-17-0805.1} or see the full citation reference in the bibliography under \citet{DossGollin:2018bn}.

Codes used to build this paper are available at \url{https://github.com/jdossgollin/2018-paraguay-floods}.

@@

\begin{figure}
	\centering
	\includegraphics[width=6.5in]{study_area.jpg}
	\caption{
		Topographical map of the study area.
		Colors indicate $\log_{10}$ of elevation, in \si{\meter}, from the Global Land One-Km Base Elevation project available at \texttt{http://iridl.ldeo.columbia.edu/SOURCES/.NOAA/.NGDC/.GLOBE/.topo/}.
		(a): all of South America.
		The domains of the \acrlong{lprb} and the domain used for weather typing are indicated in red and blue, respectively.
		(b): The \acrfull{lprb}.
		As for (a), the \gls{lprb} is marked with a red box.
		Streamflow time series shown in \cref{fig:streamflow} were taken from the fours stations indicated.
		The Paraguay River and its tributaries, from the Natural Earth database (\texttt{www.naturalearthdata.com}), are also shown.
		Full station names are: Bah\'ia Negra (Bne); Concepci\'on (Conc); Asunci\'on (Asu); Pilar (Pil).
	}\label{fig:study-area}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=6.5in]{anomalies_ndjf1516.pdf}
	\caption{
		Monthly composite anomalies observed during NDJF 2015-16.
		Top row (a-d) shows streamfunction anomalies at \SI{850}{\hecto\pascal}.
		Bottom row (e-h) shows rainfall anomalies, in units of \si{\milli\meter\per\day}.
	}\label{fig:anomalies}
\end{figure}

>>>>

% Page setup
\usepackage[
    margin=0.9in
]{geometry}

@@

\usepackage[acronym,toc,nopostdot,nonumberlist]{glossaries}
\makeglossaries
\newacronym{cca}{CCA}{canonical correlation analysis}
\newacronym{ecmwf}{ECMWF}{European Centre for Medium-Range Weather Forecasts}
\newacronym{enso}{ENSO}{El Ni\~{n}o-Southern Oscillation}
\newacronym{eof}{EOF}{empirical orthogonal function}
\newacronym{iri}{IRI}{International Research Institute for Climate and Society}
\newacronym{hxlr}{HXLR}{heteroscedastic extended logistic regression}
\newacronym{lprb}{LPRB}{Lower Paraguay River Basin}
\newacronym{mjo}{MJO}{Madden-Julian Oscillation}
\newacronym{mos}{MOS}{model output statistics}
\newacronym{sallj}{SALLJ}{South American low-level jet}
\newacronym{pcr}{PCR}{principal components regression}
\newacronym{s2s}{S2S}{sub-seasonal to seasonal}
\newacronym{sacz}{SACZ}{South Atlantic Convergence Zone}
\newacronym{scad}{SCAD}{South Central Atlantic Dipole}
\newacronym{sst}{SST}{sea-surface temperature}
\newacronym{xlr}{XLR}{homoscedastic extended logistic regression}
\newacronym{wt}{WT}{weather type}

@@

\date{}
\title{Heavy rainfall in Paraguay during the 2015-2016 austral summer: causes and sub-seasonal-to-seasonal predictive skill}
\author[1,2]{James Doss-Gollin\thanks{\href{mailto:james.doss-gollin@columbia.edu}{james.doss-gollin@columbia.edu}}}
\author[3,4]{\'{A}ngel G. Mu\~{n}oz}
\author[4]{Simon J. Mason}
\author[5,6]{Max Past\'{e}n}
\affil[1]{Department of Earth and Environmental Engineering, Columbia University}
\affil[2]{Columbia Water Center}
\affil[3]{Atmospheric and Oceanic Sciences (AOS), Princeton University}
\affil[4]{International Research Institute for Climate and Society (IRI), The Earth Institute, Columbia University.}
\affil[5]{Direcci\'{o}n de Meteorolog\'{i}a e Hidrolog\'{i}a, Paraguay}
\affil[6]{Facultad Polit\'ecnica, Universidad Nacional de Asunci\'{o}n, Paraguay}

@@

This is a post-print of the paper ``Heavy rainfall in Paraguay during the 2015-16 austral summer: causes and sub-seasonal-to-seasonal predictive skill'', by James Doss-Gollin, \'{A}ngel G. Mu\~{n}oz, Simon J. Mason, and Max Past\'{e}n, published in Journal of Climate.
You can find the final, type-set version at \url{https://journals.ametsoc.org/doi/abs/10.1175/JCLI-D-17-0805.1} or see the full citation reference in the bibliography under \citet{DossGollin:2018bn}.

Codes used to build this paper are available at \url{https://github.com/jdossgollin/2018-paraguay-floods}.
Comments to the authors may be directed to James Doss-Gollin: \href{mailto:james.doss-gollin@columbia.edu}{james.doss-gollin@columbia.edu}

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{study_area.jpg}
	\caption{
		Topographical map of the study area.
		Colors indicate $\log_{10}$ of elevation, in \si{\meter}, from the Global Land One-Km Base Elevation project available at \texttt{http://iridl.ldeo.columbia.edu/SOURCES/.NOAA/.NGDC/.GLOBE/.topo/}.
		(a): all of South America.
		The domains of the \acrlong{lprb} and the domain used for weather typing are indicated in red and blue, respectively.
		(b): The \acrfull{lprb}.
		As for (a), the \gls{lprb} is marked with a red box.
		Streamflow time series shown in \cref{fig:streamflow} were taken from the fours stations indicated.
		The Paraguay River and its tributaries, from the Natural Earth database (\texttt{www.naturalearthdata.com}), are also shown.
		Full station names are: Bah\'ia Negra (Bne); Concepci\'on (Conc); Asunci\'on (Asu); Pilar (Pil).
	}\label{fig:study-area}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=6.5in]{anomalies_ndjf1516.pdf}
	\caption{
		Monthly composite anomalies observed during NDJF 2015-16.
		Top row (a-d) shows streamfunction anomalies at \SI{850}{\hecto\pascal}.
		Bottom row (e-h) shows rainfall anomalies, in units of \si{\milli\meter\per\day}.
	}\label{fig:anomalies}
\end{figure}
